### 2024-03-26 doc/sections/mav-syntax.tex
[ tex ] semantics semantics semantics
Rephrase equivalence

The structures of MAV are formed from positive and negative atoms ($\vPos\vA$ and $\vNeg\vA$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
\begin{displaymath}
  \vP,\vQ,\vR,\vS
  \Coloneq \vPos\vA
  \mid     \vNeg\vA
  \mid     \vUnit
  \mid     \vP\vSeq \vQ
  \mid     \vP\vTens\vQ
  \mid     \vP\vParr\vQ
  \mid     \vP\vWith\vQ
  \mid     \vP\vPlus\vQ
\end{displaymath}
Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective seq.
\begin{displaymath}
  \begin{array}{
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l}
    \vDual{\vPos\vA}     & \vNeg\vA
                         &
    \vDual{\vUnit}       & \vUnit
                         &
    \vDual{\vP\vTens\vQ} & \vDual\vP \vParr \vDual\vQ
                         &
    \vDual{\vP\vParr\vQ} & \vDual\vP \vTens \vDual\vQ
    \\
    \vDual{\vNeg\vA}     & \vPos\vA
                         &
    \vDual{\vP\vSeq \vQ} & \vDual\vP \vSeq  \vDual\vQ
                         &
    \vDual{\vP\vWith\vQ} & \vDual\vP \vPlus \vDual\vQ
                         &
    \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
  \end{array}
\end{displaymath}

Equivalences:
\begin{displaymath}
  \begin{array}{
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll}
    \vP\vSeq\vUnit
     & \vP
     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
     &
    \vUnit\vSeq\vP
     & \vP
     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
     &
    \vP\vSeq(\vQ\vSeq\vR)
     & (\vP\vSeq\vQ)\vSeq\vP
     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
    \\
    \vP\vTens\vUnit
     & \vP
     & \RuleLabel*[tens-unit]{\vTens-Unit}
     &
    \vP\vTens\vQ
     & \vQ\vTens\vP
     & \RuleLabel*[tens-comm]{\vTens-Comm}
     &
    \vP\vTens(\vQ\vTens\vR)
     & (\vP\vTens\vQ)\vTens\vP
     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
    \\
    \vP\vParr\vUnit
     & \vP
     & \RuleLabel*[parr-unit]{\vParr-Unit}
     &
    \vP\vParr\vQ
     & \vQ\vParr\vP
     & \RuleLabel*[parr-comm]{\vParr-Comm}
     &
    \vP\vParr(\vQ\vParr\vR)
     & (\vP\vParr\vQ)\vParr\vP
     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
  \end{array}
\end{displaymath}

>>>>

The structures of MAV are formed from positive and negative atoms ($\vPos\vA$ and $\vNeg\vA$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
\begin{displaymath}
  \vP,\vQ,\vR,\vS
  \Coloneq \vPos\vA
  \mid     \vNeg\vA
  \mid     \vUnit
  \mid     \vP\vSeq \vQ
  \mid     \vP\vTens\vQ
  \mid     \vP\vParr\vQ
  \mid     \vP\vWith\vQ
  \mid     \vP\vPlus\vQ
\end{displaymath}
Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective seq.
\begin{displaymath}
  \begin{array}{
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l @{\hspace{1cm}}
      l@{\;=\;}l}
    \vDual{\vPos\vA}     & \vNeg\vA
                         &
    \vDual{\vUnit}       & \vUnit
                         &
    \vDual{\vP\vTens\vQ} & \vDual\vP \vParr \vDual\vQ
                         &
    \vDual{\vP\vParr\vQ} & \vDual\vP \vTens \vDual\vQ
    \\
    \vDual{\vNeg\vA}     & \vPos\vA
                         &
    \vDual{\vP\vSeq \vQ} & \vDual\vP \vSeq  \vDual\vQ
                         &
    \vDual{\vP\vWith\vQ} & \vDual\vP \vPlus \vDual\vQ
                         &
    \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
  \end{array}
\end{displaymath}
Usually, in BV and its extension, structures are considered equivalent modulo a decidable equality comprising duality, as given above, and the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a pomonoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative pomonoids.
\begin{displaymath}
  \begin{array}{
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll}
    \vP\vSeq\vUnit
     & \vP
     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
     &
    \vUnit\vSeq\vP
     & \vP
     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
     &
    \vP\vSeq(\vQ\vSeq\vR)
     & (\vP\vSeq\vQ)\vSeq\vP
     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
    \\
    \vP\vTens\vUnit
     & \vP
     & \RuleLabel*[tens-unit]{\vTens-Unit}
     &
    \vP\vTens\vQ
     & \vQ\vTens\vP
     & \RuleLabel*[tens-comm]{\vTens-Comm}
     &
    \vP\vTens(\vQ\vTens\vR)
     & (\vP\vTens\vQ)\vTens\vP
     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
    \\
    \vP\vParr\vUnit
     & \vP
     & \RuleLabel*[parr-unit]{\vParr-Unit}
     &
    \vP\vParr\vQ
     & \vQ\vParr\vP
     & \RuleLabel*[parr-comm]{\vParr-Comm}
     &
    \vP\vParr(\vQ\vParr\vR)
     & (\vP\vParr\vQ)\vParr\vP
     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
  \end{array}
\end{displaymath}
